### 2020-08-27 5_evaluation.tex
Update number of systems in validation comparison.

Table~\ref{tab:metg-predict-strong} expands this comparison to the 4
patterns tested in Section~\ref{subsec:scalability} for all 11
programming systems that scale well enough to evaluate the separation
between the limit-ideal and limit-actual intersections. We see that
overall, the mean separation is at most $1.96\times$ in node count
and at most $1.29\times$ in time to solution, making this a
useful way to predict strong scaling in the 4 patterns we tested in
Section~\ref{subsec:scalability}.

\zap{
When we consider all 11 programming systems that scale well enough to
perform this experiment, we find that the average separation between
the ideal and actual intersection points is $1.61\times$ in node count
(max $2.19\times$, min $1.13\times$) and $1.28\times$ in time to
solution (max $1.69\times$, min $1.01\times$).
}

>>>>

Table~\ref{tab:metg-predict-strong} expands this comparison to the 4
patterns tested in Section~\ref{subsec:scalability} for all 12
programming systems that scale well enough to evaluate the separation
between the limit-ideal and limit-actual intersections. We see that
overall, the mean separation is at most $1.96\times$ in node count
and at most $1.29\times$ in time to solution, making this a
useful way to predict strong scaling in the 4 patterns we tested in
Section~\ref{subsec:scalability}.

### 2020-08-27 e11_metg_predict_strong.tex
Update figure placement and performance numbers.
Update number of systems in validation comparison.

\begin{table}[t]
\centering
\small
\begin{tabular}{r | c | c | c | c}
        & \multicolumn{2}{|c|}{Nodes} & \multicolumn{2}{|c}{Time to Solution} \\
Pattern & mean & std.~dev. & mean & std.~dev. \\
\hline
stencil & $1.61\times$ & 0.324 & $1.29\times$ & 0.238 \\
nearest & $1.77\times$ & 0.253 & $1.24\times$ & 0.310 \\
spread  & $1.39\times$ & 0.322 & $1.30\times$ & 0.171 \\
nearest, 4 graphs & $2.15\times$ & 0.635 & $1.42\times$ & 0.723
\end{tabular}

\vspace{-0.20cm}
\caption{Average factor of separation between limit-ideal and limit-actual intersection across the 4 patterns tested in Section~\ref{subsec:scalability}.\label{tab:metg-predict-strong}}
\vspace{-0.5cm}
\end{table}

>>>>

\begin{table}[t]
\centering
\small
\begin{tabular}{r | c | c | c | c}
        & \multicolumn{2}{|c|}{Nodes} & \multicolumn{2}{|c}{Time to Solution} \\
Pattern & mean & std.~dev. & mean & std.~dev. \\
\hline
stencil & $1.64\times$ & 0.278 & $1.26\times$ & 0.246 \\
nearest & $1.75\times$ & 0.268 & $1.15\times$ & 0.331 \\
spread  & $1.43\times$ & 0.288 & $1.29\times$ & 0.206 \\
nearest, 4 graphs & $1.96\times$ & 0.680 & $1.26\times$ & 0.702
\end{tabular}

\vspace{-0.20cm}
\caption{Factor of separation between limit-ideal and limit-actual intersections across all 12 programming systems tested in Section~\ref{subsec:scalability}.\label{tab:metg-predict-strong}}
\vspace{-0.5cm}
\end{table}
